Order reduction and partial MILP models \\ for certifying Robustness of DNNs globally.

### 2025-07-29 AAAI2026/Lipitschz.tex
update a trick
Update Lipitschz.tex
update table
update
commit

@@

	\end{tabular}
	\caption{Comparison of "1v", "3v" and "2v" models 
	to obtain bounds on $\beta^{0.5}_{0,1}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of ??s, and ??s , where ??,  or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
\end{table}

>>>>

	\input{a_trick}

@@

		1v, $500 \times 1$ & 1.508 & 0.1856 & 0.0575 & 14400 \\\hline 
		3v, $500 \times 3$ & 1.256 & 0.1336 & 0.0950 & 14400 \\\hline 
	 2v, $500 \times 2$ & 1.2417 & 0.0224 & 0.0224 & 14400 \\\hline\hline

	\end{tabular}
	\caption{Comparison of "1v", "3v" and "2v" models 
	to obtain bounds on $\beta^{.5}_{0,1}$ on the {\bf 20 dimension}  reduced order MNIST DNN, for timeouts of ??s, and ??s , where ??,  or 500 ($\times 1$, $\times 2$, $\times 3$) neurons use binary variables.}
\end{table}
